Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-15 doc/paper.tex
Mićkove popravke

	\begin{algorithm}[!t]
		\caption{Discretization $D(P)$ of polygon $P$}\label{alg:discret}
		\begin{algorithmic}[1]
			\State \textbf{Input:} The set of vertices $V$ of polygon $P$
			\State \textbf{Output:} The discretization $D(P)$ of polygon $P$
			\State $BB \gets bounding\_box(P);$
			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
			\State $D(P) \gets D(BB) \cap P;$
			\State $D(P) \gets D(P) \cup V;$
		\end{algorithmic}
	\end{algorithm}
The algorithm further forms the whole regular grid of the bounding box (line 5 of the pseudocode) and finally, all points of the regular grid that belong to $P$ and all vertices of $P$ are added into the discrete set $D(P)$.

@@

	\section{Exact methods}
	In this section we present the exact ILP,  initially developed for MWSCP from~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
	\subsection{Integer linear programming model}
	Let us suppose we are given a polygon $P$ with weights assigned to vertices and the discretization $D(P)$ of $P$.  The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
	The problem is related to the known MWSCP  as follows.
	Family $\mathcal{F}$ of nonempty sets consists of the sets
	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$.  For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.  In this way, our starting task is equivalent of finding a  covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$ of minimum weight, that is
	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that

$$f(\mathcal{C}) = \sum_{S_i \in \mathcal{C}} c(S_i)$$

@@

      After conducting preliminary results, for
        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$.

>>>>

	\begin{algorithm}[!t]
		\caption{Discretization $D(P)$ of polygon $P$}\label{alg:discret}
		\begin{algorithmic}[1]
			\State \textbf{Input:} The set of vertices $V$ of polygon $P$
			\State \textbf{Output:} The discretization $D(P)$ of polygon $P$
			\State $BB \gets bounding\_box(P);$
			\State $\bigtriangleup_{x},\bigtriangleup_{y} \gets resolution(P);$
			\State $D(BB) \gets regular\_grid(BB,\bigtriangleup_{x},\bigtriangleup_{y});$
			\State $D(P) \gets D(BB) \cap interior(P);$
			\State $D(P) \gets D(P) \cup V;$
		\end{algorithmic}
	\end{algorithm}
The algorithm further forms the whole regular grid of the bounding box (line 5 of the pseudocode) and finally, all points of the regular grid that belong to interior of $P$ and all vertices of $P$ are added into the discrete set $D(P)$.

@@

	\section{Exact methods}
	In this section we present the exact ILP,  initially developed for MWSCP from~\cite{vazirani2013approximation} and \emph{Constraint Programming} (CP) models for solving WOAGP  under regular grid discretization, which are used  in the rest of the paper.
	\subsection{Integer linear programming model}
	Let us suppose we are given a polygon $P$ with weights assigned to vertices and the discretization $D(P)$ of $P$.  The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
	The problem is related to the known MWSCP  as follows.
	Family $\mathcal{F}$ of nonempty sets consists of the sets
	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$.  For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.  In this way, our starting task is equivalent of finding a  covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$ of minimum weight, that is
	$$ \bigcup_{S \in \mathcal{C}} S = D(P),$$ such that

$$f(\mathcal{C}) = \sum_{S \in \mathcal{C}} c(S)$$

@@

      After conducting preliminary results, for
        \textsc{Greedy + \textsc{Cplex}} we decided to set up $K = \lceil 0.05 \cdot n \rceil$ in order to allow less computational time of the hybrid than the average runtime of the pure greedy method.
